The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-05-01 article.tex
Consistency

While the CDK has purported to be a general purpose cheminformatics
toolkit, older versions were designed by a community with specific
applications in mind, primary among them being structure elucidation. In
addition, an implicit goal of previous versions was to have the CDK
serve as an educational resource to enable students of cheminformatics
to understand the underlying algorithms. This resulted in certain
functionalities, such as fingerprinting~\cite{Clark2014,Cannon2006},
receiving more attention than others, such as stereochemistry. The
outcome was significant variance in performance and features
throughout the toolkit.

>>>>

While the CDK has purported to be a general purpose cheminformatics
toolkit, older versions were designed by a community with specific
applications in mind, primary among them being structure elucidation. In
addition, an implicit goal of previous versions was to have the CDK
serve as an educational resource to enable students of cheminformatics
to understand the underlying algorithms. This resulted in certain
functionalities, such as molecular fingerprinting~\cite{Clark2014,Cannon2006},
receiving more attention than others, such as stereochemistry. The
outcome was significant variance in performance and features
throughout the toolkit.
